### 2017-08-18 pkg/model4you/inst/JORS/man_model4you.Rnw
update plot fcts and add plot for logistic regression
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1534 255f4249-2263-4417-b1ea-8498779e27a7

The model can be visualised by plotting the estimated densities
(see Figure~\ref{fig:math_bmod_vis}):
<<math_bmod_vis, fig.height = 3, out.width = '0.7\\textwidth', fig.cap = "Base model for Mathematics Exam data.">>=  
lmplot(bmod_math)
@

A tree based on this model can be computed and visualised in only two lines of
code:
<<math_tree, fig.width = 13, fig.cap = "Personalised model tree for math exam.">>=  
tr_math <- pmtree(bmod_math, control = ctree_control(maxdepth = 2))
plot(tr_math, terminal_panel = node_pmterminal(tr_math, plotfun = lmplot))
@

>>>>

The model can be visualised by plotting the estimated densities
(see Figure~\ref{fig:math_bmod_vis} (a)):
<<eval=FALSE>>=  
lm_plot(bmod_math)
@

As the plot is a \emph{ggplot2} graphic it can be maniulated with the usual
\emph{ggplot2} layers, e.g.\ with
<<eval=FALSE>>=
lm_plot(bmod_math) + labs(y = "Estimated Density", x = "% Correct")
@
or equivalently with 
<<eval=FALSE>>=
myplot <- function(model, ...) {
  lm_plot(model, ...) + 
    labs(y = "Estimated Density", x = "% Correct")
}
myplot(bmod_math)
@
The result is shown in Figure~\ref{fig:math_bmod_vis} (b).
<<math_bmod_vis, echo=FALSE, fig.cap = "Base model for Mathematics Exam data.", fig.subcap=c("Figure made with \\texttt{lm\\_plot()}.", "Figure made with manipulated \\texttt{lm\\_plot()}."), out.width="0.45\\textwidth", fig.height=3, fig.width=5>>=
lm_plot(bmod_math)
myplot <- function(model, ...) {
  lm_plot(model, ...) + 
    labs(y = "Estimated Density", x = "% Correct")
}
myplot(bmod_math)
@

A tree based on this model can be computed and visualised in only two lines of
code:
<<math_tree, fig.width = 13, fig.cap = "Personalised model tree for math exam.">>=  
tr_math <- pmtree(bmod_math, control = ctree_control(maxdepth = 2))
plot(tr_math, terminal_panel = node_pmterminal(tr_math, plotfun = myplot))
@
